---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# libminer

<!-- badges: start -->
[![R-CMD-check](https://github.com/awesomecosmos/libminer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/awesomecosmos/libminer/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of libminer is to provide utility functions for inspecting and examining your local R package installations.

This is a R package developed as part of my workshop participation in '[Fundamentals of R Package Development](https://posit-conf-2023.github.io/pkg-dev/)' at the [Posit Conference 2023](https://posit.co/conference/)! Credit for this package and its code goes to [@ateucher](https://github.com/ateucher).

## Installation

You can install the development version of libminer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("awesomecosmos/libminer")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(libminer)

lib_summary()

# can also calculate total file sizes
# lib_summary(sizes = TRUE)
```
